Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-25 paper.tex
Tweaks

\subsection{Case study: All of Us exome-like data}
The All of Us dataset comprises 245,388 clinical-grade whole genome sequences (WGS),
identifying over 1 billion variants, including 3.9 million novel variants
with coding consequences~\citep{all2024genomic}. Participants are from the United States,
with an emphasis on historically underrepresented genetic ancestry groups.
The genomic data, generated through short-read sequencing on the Illumina NovaSeq 6000,
is of high quality, with an average coverage depth of 30x, and is linked to extensive
health-related information, providing a valuable resource for biomedical research.
WGS analysis is conducted on the Illumina DRAGEN platform, with alignment performed
using the GRCh38dh reference genome. GTC files are converted to VCF format using
Picard GtcToVcf, and every step of the WGS procedure is rigorously controlled by
predefined quality control measures.

@@

\begin{table}
\caption{Summary for VCF Zarr conversion of the Norway spruce
WGS data on all 12 autosomes (1,063 samples, 374,517,0452 variants)
consisting of 34 fields and 2.3TiB of storage ($\sim 3.2X$ smaller 
than source gzipped VCFs). The chunk size is 10,000 variants times 
1,063 samples (i..e, a single sample chunk). This uses local 
alleles to reduce the 
space required by the PL field; see the text for discussion.
For column details see the caption of
Table~\ref{tab-genomics-england-data}.
\label{tab-spruce-data}}

>>>>

\subsection{Case study: All of Us exome-like data}
The All of Us dataset comprises 245K clinical-grade whole genome sequences,
identifying over 1 billion variants, including 3.9 million novel variants
with coding consequences~\citep{all2024genomic}. Participants are from the United States,
with an emphasis on historically underrepresented genetic ancestry groups.
The genomic data, generated through short-read sequencing on the Illumina NovaSeq 6000,
is of high quality, with an average coverage depth of 30x, and is linked to extensive
health-related information, providing a valuable resource for biomedical research.
WGS analysis is conducted on the Illumina DRAGEN platform, with alignment performed
using the GRCh38dh reference genome. GTC files are converted to VCF format using
Picard GtcToVcf, and every step of the WGS procedure is rigorously controlled by
predefined quality control measures.

@@

\begin{table}
\caption{Summary for VCF Zarr conversion of the Norway spruce
WGS data on all 12 autosomes (1,063 samples, 374,517,0452 variants)
consisting of 34 fields and 2.3TiB of storage ($\sim 3.2$X smaller 
than source gzipped VCFs). The chunk size is 10,000 variants $\times$
1,063 samples (i..e, a single sample chunk). This uses local 
alleles to reduce the 
space required by the PL field; see the text for discussion.
For column details see the caption of
Table~\ref{tab-genomics-england-data}.
\label{tab-spruce-data}}
